---
title: "Day 3 Homework"
output: html_document
---

The goal of this homework is to get practice with manipulating data.

```{r}
library(reshape2)
mydata <- read.csv("~/Desktop/r_programming_bsos/day2/ABN.csv")
mydata
```


1. Make both a "wide" and a "long" version of your data

<<<<<<< HEAD
```{r}

?melt
mydata.melt <- melt(mydata, measure.vars = c("Living.Correct", "Hard.Correct", "Fit.Correct", variable.name = "Correctness", value.name = "selection"))
# confused about variable.name and value.name
```

  - casting with a LOT of variables
```{r eval=FALSE}
mydata.wide <- dcast(mydata.long, [80 columns here] ~ split)

columns.to.keep <- colnames(mydata.long)[1:80]
columns.to.keep.pasted <- paste(colums.to.keep, collapse = "+")
my.cast.formula <- as.formula(paste(columns.to.keep.pasted, "~split"))
class(my.cast.formula) # "formula"
=======
- casting with a LOT of variables

```{r eval=FALSE}

mydata.wide <- dcast(mydata.long, [80 columns here] ~ split)

columns.to.keep <- colnames(mydata.long)[1:80]
columns.to.keep.pasted <- paste(columns.to.keep, collapse = " + ")
my.cast.formula <- as.formula(paste(columns.to.keep.pasted, " ~ split"))
class(my.cast.formula)  # "formula"
>>>>>>> 42030da807d34c34a9518434fe1abdd1af641018
mydata.wide <- dcast(mydata.long, formula = my.cast.formula)


```

<<<<<<< HEAD

=======
>>>>>>> 42030da807d34c34a9518434fe1abdd1af641018
2. Transform a variable

```{r}
mydata
mydata$Delayed.Raw2 <- mydata$Delayed.Raw * 100
mydata$Delayed.Raw2
mydata
```


3. Recode a factor

```{r}
mydata$Age_Years <- as.factor(mydata$Age_Years)
mydata$Age_Years
summary(mydata$Age_Years)
levels(mydata$Age_Years)
levels(mydata$Age_Years) <- c("5yo", "6yo", "7yo", "8yo")
levels(mydata$Age_Years)


```

4. Add a new factor, where the levels are conditional on the values of some other variable. E.g., a factor of "high", "medium", and "low" based on thresholds for another variable.

```{r}
?as.numeric
mydata$Total.Correct <- as.numeric(mydata$Total.Correct)
summary(mydata$Total.Correct)
mydata$accuracy <- "medium"
mydata$accuracy[mydata$Total.Correct < 10] <- "high"
mydata$accuracy[mydata$Total.Correct > 5] <- "low"
mydata$accuracy <- as.factor(mydata$accuracy)
summary(mydata$accuracy)
levels(mydata$accuracy)

```


5. Reorder the levels of this new factor

```{r}
?factor
levels(mydata$accuracy)
mydata$accuracy <- factor(mydata$accuracy, levels = c("low", "high"))
levels(mydata$accuracy)

```

# unsure how to do next steps

6. Choose a factor that could be re-coded as multiple dimensions (recall the sepal/petal vs. length/width breakdown). If you don't have one, try to create one.  Now create two (or more) new factors that represent these dimensions.

7. Using `dcast`, aggregate some variable into "cell means" of some kind.

8.  Save all of the above in a well-documented R Markdown document.  Email me the .Rmd file (and if you use different or updated data from Day 2 Homework, send that to me, too).
